### 2020-04-21 Thesis-Chapter2-Background.tex
CW2 intro reword

Two developments paved the way for \ac{the-cw2}. The first was actually a non-development: when the Clinton
administration changed its encryption policy, the U.S. House dropped the \ac{SAFEAct} \cite{goodlatte_hr3011_1996}. The
\ac{PROCODEAct} and other encryption-related bills went un-passed as well \cite{burns_s1726_1996} \cite{leahy_s376_1997}
\cite{ashcroft_s2067_1998} \cite{goss_hr2616_1999} \cite{goss_hr2617_1999} \cite{administration_CESA_1999}
\cite{leahy_s3083_2000}. This legislative failure meant that rather than being written in the pen of law, encryption
policy was written in the pencil of executive order.

@@

\subsubsection{Failed U.S. Regulation Attempts}

@@

>>>>

Two developments paved the way for \ac{the-cw2}. The first was actually a non-development: when the Clinton
administration changed its encryption policy, the U.S. House dropped the \ac{SAFEAct} \cite{goodlatte_hr3011_1996}. The
\ac{PROCODEAct} and other encryption-related bills went un-passed as well, as elaborated in \mysec{sec-us-reg-fails}.
This legislative failure meant that rather than being written in the pen of law, encryption policy was written in the
pencil of executive order.

@@

\subsubsection{Failed U.S. Regulation Attempts}
\label{sec-us-reg-fails}

@@

% \cite{burns_s1726_1996} \cite{leahy_s376_1997} \cite{ashcroft_s2067_1998} \cite{goss_hr2616_1999}
% \cite{goss_hr2617_1999} \cite{administration_CESA_1999} \cite{leahy_s3083_2000}
